---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/img/",
  eval=TRUE,
  dpi = 150,
  fig.width = 5,
  fig.height = 3.2
)
library(ggplot2)
tt <- theme_get() +
  theme(legend.position = c(0.98, 0.97),
        legend.justification = c(1, 1),
        text = element_text(size = 9.5),
        axis.title = element_text(size = 11))
theme_set(tt)
```

popmods
=========

Easy numerical analysis of continuous-time population models in ecology.

Models currently supported:

- logistic growth
- delayed-logistic growth
- Lotka Volterra (predator-prey)
- Lotka Volterra (two-species competition)
- rock-paper-scissors intransitive competition
- rock-paper-scissors-lizard-spock
- SIR epidemiological model

## Installation

Install the development version from GitHub with:

```{r, eval=FALSE}
devtools::install_github("patrickbarks/popmods")
#
# or
#
install.packages("remotes") # smaller and quicker to install than devtools
remotes::install_github("patrickbarks/popmods")
```

## Usage

```{r, message=FALSE}
devtools::load_all("~/popmods")
library(ggplot2)

# vector of time points at which to evaluate models
t <- seq(0, 50, 0.01)
```

##### Delayed logistic

```{r Delayed-logistic}
df_dl <- logistic_delay(time = t, init_n = 10, r = 1.1, k = 500, tau = 1.12)

ggplot(df_dl, aes(time, abundance)) +
  geom_line(lwd = 1.5)
```


##### Lotka-Volterra predator-prey

```{r Lotka-Volterra-predator-prey}
df_lvpp <- lotka_volterra(time = t, init_n = 50, init_p = 30, r = 0.8, c = 0.04,
                          a = 0.2, m = 0.3)

ggplot(df_lvpp, aes(time, abundance, color = population)) +
  geom_line(lwd = 1.5) +
  scale_color_brewer(type = 'qual', palette = 6)
```

##### Rock-paper-scissors-lizard-spock competition

```{r R-P-S-L-K-competition}
df_rpslk <- rpslk(time = t, init_r = 0.02, init_p = 0.02, init_s = 0.03,
                  init_l = 0.9, init_k = 0.03, b = 0.7)

ggplot(df_rpslk, aes(time, proportion, color = strategy)) +
  geom_line(lwd = 1.5) +
  scale_color_brewer(type = 'qual', palette = 6)
```

##### SIR epidemiological model

```{r SIR-epidemiological-model}
df_sir <- sir(time = t, init_s = 0.9999, init_i = 0.0001, init_r = 0,
              gamma = 0.6, beta = 0.08)

ggplot(df_sir, aes(time, proportion, color = status)) +
  geom_line(lwd = 1.5) +
  scale_color_brewer(type = 'qual', palette = 6)
```


## Contributions

All contributions are welcome. Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

